### 2018-01-11 readme.Rmd
Updates based on reviewer comments #5

or the development version with devtools:
```{r devtools, eval = FALSE}
install.packages("devtools")
devtools::install_github('lebebr01/highlightHTMl')
```

@@

As mentioned above, text and summary tables can be styled using CSS ids. The CSS ids are inserted into text by using braces (i.e. \{) with a CSS id hashtag following the opening brace (e.g. \{#bggrey example\}). In the previous example, the word "example" would be identified with the CSS id #bggrey and could be styled using CSS.

@@

## Simple Example of Package Workflow

>>>>

or the development version with devtools:
```{r devtools, eval = FALSE}
install.packages("devtools")
devtools::install_github('lebebr01/highlightHTML')
```

@@

As mentioned above, text and summary tables can be styled using CSS ids or classes. The CSS ids (or classes) are inserted into text by using braces (i.e. \{) with a CSS id hashtag following the opening brace (e.g. `\{#bggrey example\}`). In the previous example, the word "example" would be identified with the CSS id #bggrey and could be styled using CSS.

@@

## Adding CSS ids manually
Suppose you have a summary table like the following (note: this table was created by typing manually, a more typical workflow is shown later using R directly):

| Color Name | Number       |
|----------- | ------------ |
| Red        |  25          |
| Blue       |  40          |
| Green      |  4           |
| Orange     |  87          |

You could then add styling by adding the following tags to the table, again this was added by hand, but a conditional example with R is shown later.

| Color Name | Number       |
|----------- | ------------ |
| Red        |  25  #bgred  |
| Blue       |  40  #bgblue |
| Green      |  4           |
| Orange     |  87          |

The addition of the *#bgblue* and *#bgred* indicates which cells will be changed. After turning the markdown document into an html file, this package can now be used to post-process the html file. The post-processing will add an id value for each cell with the *#bgblue* or *#bgred* and remove those from the table.

The CSS for these ids could be as simple as the following to change the background color of the cells with the CSS id inserted above:

````
#bgred {background-color: #FF0000;}
#bgblue {background-color: #0000FF;}
````

## Simple Example of Common Package Workflow
